\documentclass[10pt,a4paper,sans]{moderncv} 
\moderncvstyle{classic}                    
\moderncvcolor{purple}                    
\usepackage[utf8]{inputenc}              
\usepackage{expl3}
\usepackage{multicols}
\expandafter\def\csname ver@l3regex.sty\endcsname{}
\usepackage[scale=0.77]{geometry}
\setlength{\hintscolumnwidth}{3cm}     
\name{Eryk}{Warchulski}
\address{github.com/warbarbye \\ + 48 697 291 468 \\ ewarchul@gmail.com}{}
%\phone{+48 697 291 468}          
%\email{ewarchul@gmail.com}              
\begin{document}
\makecvtitle
\section{Education}
\cventry{2015-2019}{Bachelor}{Warsaw University of Technology, Faculty of Electronics and Information Technology}{Warsaw - Poland}{\textit{Electronics}}{} 
\cventry{2019-2020}{Master of science}{Warsaw University of Technology, Faculty of Electronics and Information Technology}{Warsaw - Poland}{\textit{Computer science}}{} 

\section{Experience}
\cventry{\small{06.2018-09.2018}}{Data Engineer, Internship}{Poland's Ministry of Finance}{Warsaw}{}{
  Project focused on a social network analysis (\texttt{Python}, \texttt{R} and \texttt{Neo4j} graph database)
}
\cventry{\small{02.2019-$\dots$}}{Machine Learning Engineer}{Warsaw University of Technology}{Warsaw}{}{
   I participate in science and research project which is focusing on the optimization of energy consumption of cooling system for external 
   company.
}
\cventry{\small{08.2019-01.2020}}{Data Scientist}{Polskie Technologie Sp. z o. o., \texttt{PLTE}}{Warsaw}{}{
  I worked as a DS and a partial DevOps Engineer for fin-tech company which is focusing on fincial risk modelling. 
}
\section{Programming}
\cvitem{\textbf{R}}{full \texttt{Tidyverse} stack, \texttt{rlang}, \texttt{mlr/3}, \texttt{drake}, \texttt{RMarkdown}, \texttt{optim}, \texttt{caret}, \texttt{R6} class system}
\cvitem{\textbf{Python}}{\texttt{Numpy}, \texttt{Tensorflow}, \texttt{Keras}, \texttt{Spade}}
\cvitem{\textbf{Haskell}}{\texttt{Stack}, \texttt{QuickCheck}, general notion of functional programming i.e functors, applicative, monads, etc.}
\cvitem{\textbf{C}}{System programming, \texttt{Posix}}
\cvitem{\textbf{C++}}{\texttt{STL}, generic programming, \texttt{C++11}}
\cvitem{\textbf{Elixir}}{beginner, learning in progress!}
\section{Technologies}
\cvitem{\textbf{Database}}{\texttt{SQL}, \texttt{SQLite}, \texttt{Neo4j}, \texttt{Redis}}
\cvitem{\textbf{Docker}}{\texttt{Docker Compose}}
\cvitem{\textbf{git}}{GitHub, GitLab and Bitbucket ecosystem i.e. Travis, GitLab CI/CD, Jira}
\cvitem{\textbf{Unix/Linux}}{advanced as a user and system administrator}
\cvitem{\textbf{Literal programming}}{\texttt{Jupyter ecosystem}}
\cvitem{\textbf{Formal specification}}{\texttt{Alloy}}
\cvitem{\textbf{Methodoglies}}{Scrum, Kanban}
\newpage
\section{Publications}
\cvitem{PPSN2018}{"Improving the Differential Evolution Strategy by coupling it with CMA-ES", Jaroslaw Arabas, Eryk Warchulski and Dariusz Jagodzinski}
\cvitem{ELTE2019}{"Optimization of ultra-thin magnetron sputtered aluminium films", Robert Mroczynski, Jaroslaw Arabas, Eryk Warchulski}
\cvitem{PPSN2020}{"Investigation of step-size adaptation methods for CMA-ES based on population midpoint fitness"}
\section{Engineering \& science intrests}
\begin{multicols}{2}
\begin{itemize}
\item{Functional programming}
\item{Optimization}
\item{Nonparametric regression} 
\item{Evolutionary strategies}
\end{itemize}
\end{multicols}
\section{Projects (on my GitHub!)}
\cvitem{\textbf{R}}{Modified regression random forest from scratch – modification concerns on selecting instances from dataset using kernel density estimate.}
\cvitem{\textbf{R}}{Tools for and analysis of unsupervised novelty detection methods.}
\cvitem{\textbf{Python}}{Convolutional neural network from scratch.}
\cvitem{\textbf{Python}}{Multiagent trade market simulator.}
\cvitem{\textbf{C++}}{Efficient generator of Barabasi-Albert random graphs.}
\cvitem{\textbf{Haskell}}{Pyramid puzzle solver.}
\section{Languages}
\cvitemwithcomment{Polish}{Native}{}
\cvitemwithcomment{English}{Intermediate}{fluent reading and writing, good at verbal}
\clearpage
\end{document}
